Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-06-01 paper.tex

\section{Method}

@@

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
  		\caption{Random Unreal method}
  		\label{fig:Random-Unreal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
  		\caption{Complete Columns method}
  		\label{fig:Columns-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
  		\caption{Complete Rows method}
  		\label{fig:Rows-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
		\caption{Random Subjects method}
  		\label{fig:Uniform-S-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
  		\caption{(Uniform) method }
  		\label{fig:Diagonal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
  		\caption{(Triangular-L) method}
  		\label{fig:triangular-L-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
  		\caption{(Triangular-S) method}
  		\label{fig:triangular-S-Sample-Training-set}
	\end{subfigure}
	\caption{Sample training set for different methods with a training ratio of 0.4.}		
\end{figure}

>>>>

\section{Method}
To evaluate the reproducibility of a pipeline, a retrieved matrix from 
the subjects and file-ids is built. Subjects and file-ids are equivalent 
to users and items, respectively, as they are known in Collaborative Filtering (CF) technique.
Filling in the missing entries of this matrix encompasses some issues 
which take some barriers for use of Collaborative filtering technique as it 
has being used in e-commerce applications.
For instance, files-ids (items) are produced in a specific order in the 
pipeline however items are sequentially independent in general use of CF in e-commerce.
This issue adds constraints on the selection of CF training set. Despite of random 
selection strategy which does not taking care of item order, we had to come up with those 
selection strategies that respect the pipeline fundamental fact about file order generation.  
The aforementioned matrix (utility matrix), con be fully completed by processing all subjects 
in pipeline however the whole processing can takes loads of time. This possibility of 
having a potential complete populated matrix means despite of potential sparse matrices 
in e-commerce case studies here the utility matrix is not sparse and 
we can decide precisely which samples we need to select as our training set selection. 
In this regard, to avoid the cold start issue we can take the first file-id of all 
subjects in order to get sure that for all subjects there is at least one 
selected element in training ratio and in the same way, all generated files 
from the process of a random subject which can guarantee that all files 
are presented in the selection set at least for once.

@@

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
  		\caption{Random Unreal method}
  		\label{fig:Random-Unreal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
  		\caption{Complete Columns method}
  		\label{fig:Columns-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
  		\caption{Complete Rows method}
  		\label{fig:Rows-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
		\caption{RS method}
  		\label{fig:Uniform-S-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
  		\caption{RFNU  method }
  		\label{fig:Diagonal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
  		\caption{RFNT-L method}
  		\label{fig:triangular-L-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
  		\caption{RFNT-S method}
  		\label{fig:triangular-S-Sample-Training-set}
	\end{subfigure}
	\caption{Sample training set for different methods with a training ratio of 0.4.}		
\end{figure}
